\vspace{1.0cm} \LARGE \bf Reassortment between influenza B lineages and the emergence of a co-adapted PB1-PB2-HA gene complex

### 2014-01-31 fluB.tex
Continued revisions.

\subsection*{Measures of diversity}
We inferred the diversity of each segment over time by plotting the most recent common ancestor of all branches existing at yearly intervals, which places an upper bound on the maximum amount of diversity existing at each time period.
In addition, we calculated mean pairwise TMRCA between branches labelled as Vic and Yam for PB1, PB2 and HA.
This gave us a measure of how much a particular segment reassorts with respect to PB1, PB2 and HA segments.
If Vic and Yam lineages of PB1, PB2 and HA segments were to be considered as being separate populations this measure would be equivalent to `between population' diversity.

@@

\subsection*{Tree to tree similarities}
We subsampled our combined posterior distribution of trees to give a total of 2700 trees.
Pairwise comparison between each pair of segments was performed by comparing trees at each MCMC state.

@@

If we are comparing TMRCAs of the same two tips in tree A and tree B we express it as $\frac{[A\_{i}:A\_{i}']+[B\_{i}:B\_{i}']}{2\times [A\_{i}:B\_{i}]}$, where [A\_{i}:B\_{i}] is $\Delta$TMRCA of a pair of tips between \textit{i}th tree derived from alignment A and \textit{i}th tree derived from alignment B and [A\_{i}:A\_{i}'] is $\Delta$TMRCA between the same pair of tips between \textit{i}th tree derived from alignment A and \textit{i}th tree derived from an independent run of alignment A, to control for variability in tree topology stability over the course of the MCMC chain caused by differences in alignment lengths used to produce the trees.

>>>>

\subsection*{Measures of diversity}
We inferred the diversity of each segment at a single point in time by estimating the date of the most recent common ancestor of all branches at yearly intervals, which places an upper bound on the maximum amount of diversity existing at each time period.
In addition, we calculated mean pairwise TMRCA between branches labelled as Vic and Yam for PB1, PB2 and HA.
This gave us a measure of how much a particular segment reassorts with respect to PB1, PB2 and HA segments.
If Vic and Yam lineages of PB1, PB2 and HA segments were to be considered as being separate populations this measure would be equivalent to `between population' diversity.

@@

\subsection*{Tree to tree similarities}
We subsampled our combined posterior distribution of trees to give a total of 2700 trees.
Pairwise comparison between each pair of segments was performed by comparing individual pairs of sampled trees.

@@

If we are comparing TMRCAs of the same two tips in tree A and tree B we express it as 
\begin{equation}
\frac{[A_{i}:A_{i}']+[B_{i}:B_{i}']}{2\times [A_{i}:B_{i}]},
\frac{[A_{i}:A_{i}']+[B_{i}:B_{i}']}{2\times [A_{i}:B_{i}]},
\end{equation}
where $f(A_i,B_j)$ is the $\Delta$TMRCA of a pair of tips between the \textit{i}th tree derived from alignment A and the \textit{j}th tree derived from alignment B and $f(A_i,A_j)$ is the $\Delta$TMRCA between the same pair of tips between \textit{i}th tree derived from alignment A and \textit{j}th tree derived from an independent run of alignment A, to control for variability in tree topology stability over the course of the MCMC chain caused by differences in alignment lengths used to produce the trees.
